\thispagestyle{empty}
\vspace*{\fill}
\centerline{\LARGE\itshape Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\nobreak
\vspace{1pc}
\begingroup\small
\leftskip=0.1\textwidth
\rightskip=\leftskip
The thesis is over. This little space, is where I am supposed to thank people for their support. So let's not overcomplicate matters unnecessarily and be quick. 

Firstly, I would like to thank my advisors, Prof. Leonardo Carminati and Dr. Silvia Resconi, for being patient while teaching me stuff and for introducing me in the ATLAS enviroment with this work. Thanks also to Maria Giulia, whose master thesis has been very explicative about the \mph analysis and a compact guideline in the writing of this manuscript. Finally, to run out the ``fourth floor'' people to thank, a mention should be given to Davide for sharing with me the harshness of the graduands office this winter.

Now let's switch to the people I met in this years during my staying in the Physics Dept. I want to thank Matteo and Stefano, for sustaining and standing me, which is not easy I suppose, and for sharing several studying and drinking sessions. Thanks to Susanna, to whom I hope to be always a ``step'' ahead, Chiara, Stefano and Elena.

%Thanks also to the person who despite the seatbacks force me to carry on making me achieved what I have and who remembers me that I always deserve better than what I get, trying to never be content.

That's it, end of the story. If I got you bored, don't blame it on me: believe me, it was not made on purpose.
\par\endgroup
\vspace{\fill}
\clearpage
\thispagestyle{empty}



